The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-09-11 paper.tex
Added to quantum simulations.

Another approach to linear optics is to pack more features known as degrees of freedom onto a single photon, and to increase the degree of control over them. It is possible to manipulate degrees of freedom like polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}. Since KLM, new proposals for linear optical quantum computations (LOQC) have surfaced \cite{bib:Nielsen04,bib:BrowneRudolph05,bib:Gimeno-Segovia15,bib:Pant17}. \sihui {Some of them support new functionalities like secure delegated quantum computations \cite{bib:Barz12,bib:Fisher14}}. Others do not promise universality in their processing, but still performs tasks such as sampling \cite{bib:Aaronson11}, \sihui{encrypted quantum walks \cite{bib:Rohde_qw12}}, and secure quantum computations \cite{bib:Tan16} that might be hard or impossible with a classical system.  Such methods open up new ways to engineer quantum states and quantum operations, and expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy.

@@

\sihui{
\subsection{Quantum simulations}
Quantum simulations is about simulating a quantum system by quantum mechanical means \cite{bib:Georgescu14}, and there are generally two approaches to achieving this. The first approach is known as digital quantum simulation and achieved by building a quantum computer from unitary gate components that are generated by a Hamiltonians of quantum processes. Progress using this approach has already been discussed in Section \ref{sec:LOQC}.The second approach is known as analog quantum simulation and involves building simpler analog devices that mimic other, perhaps less accessible, quantum systems. We focus on discussing analog quantum simulation in this section.

 Quantum interferometers have been proposed and in some cases implemented as quantum simulators. In quantum chemistry, the energy spectrum of the hydrogen molecule has been calculated using a quantum simulator comprising of a pair of entangled photons in a polarization-dependent interferometer \cite{bib:Lanyon10}. With two entangled photon pairs, valence-bond states have been simulated and a fiber-based tunable directional coupler gives analogue control over superpositions of different valence-bond states \cite{bib:Ma2011}. The model of {\sc Bosonsampling}, when coupled with two-level systems that are coupled to the ports of the quantum interferometer, simulates a general spin XY Hamiltonian \cite{bib:Olivares16}. Quantum interferometers can also be used to simulate quantum walks which in turn can be used to simulate tight-binding Hamiltonians,  bosonic-to-fermionic behavior transitions, and even anyonic behavior.
  }

>>>>

Another approach to linear optics is to pack more features known as degrees of 
freedom onto a single photon, and to increase the degree of control over them. 
It is possible to manipulate degrees of freedom like polarization, time-of-
arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, 
bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}. Since KLM, new proposals 
for linear optical quantum computations (LOQC) have surfaced 
\cite{bib:Nielsen04,bib:BrowneRudolph05,bib:Gimeno-Segovia15,bib:Pant17}. 
\sihui {Some of them support new functionalities like secure delegated quantum 
computations \cite{bib:Barz12,bib:Fisher14}}. Others do not promise 
universality in their processing, but still performs tasks such as sampling 
\cite{bib:Aaronson11}, \sihui{encrypted quantum walks \cite{bib:Rohde_qw12}}, 
and secure quantum computations \cite{bib:Tan16} that might be hard or 
impossible with a classical system.  Such methods open up new ways to engineer 
quantum states and quantum operations, and expand the toolbox of baseline 
resources we have for implementing quantum computations, which could prove 
crucial in the race to achieve quantum supremacy.

@@

\sihui{
\subsection{Quantum simulations}
Quantum simulations is about simulating a quantum system by quantum mechanical means \cite{bib:Georgescu14}, and there are generally two approaches to achieving this. The first approach is known as digital quantum simulation and achieved by building a quantum computer from unitary gate components that are generated by a Hamiltonians of quantum processes. Progress using this approach has already been discussed in Section \ref{sec:LOQC}. `The second approach is known as analog quantum simulation and involves building simpler analog devices that mimic other, perhaps less accessible, quantum systems. We focus on discussing analog quantum simulation in this section.

 Quantum interferometers have been proposed and in some cases implemented as quantum simulators. In quantum chemistry, the energy spectrum of the hydrogen molecule has been calculated using a quantum simulator comprising of a pair of entangled photons in a polarization-dependent interferometer \cite{bib:Lanyon10}. With two entangled photon pairs, valence-bond states have been simulated and a fiber-based tunable directional coupler gives analogue control over superpositions of different valence-bond states \cite{bib:Ma2011}. The model of {\sc Bosonsampling}, when coupled with two-level systems that are coupled to the ports of the quantum interferometer, simulates a general spin XY Hamiltonian \cite{bib:Olivares16}. Quantum interferometers can also be used to simulate quantum walks which in turn can be used to simulate topological phases \cite{bib:Kitagawa12}, and behavior transitions in tight-binding Hamiltonians \cite{bib:Schreiber11, bib:Sansoni12,bib:Matthews13}.
  }
